\sys: Controllable Program Regeneration

### 2025-06-17 paper/draft.tex
Add semantic line breaks
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>
Fix usepackage
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>
Format table
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>
Fill out evaluation, conclusion, and abstract
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

\usepackage{setspace}
\usepackage{enumerate}
\usepackage{algorithm2e}
\usepackage{algpseudocode}
\usepackage{graphics}
\usepackage{xparse} 
\usepackage{xspace}
\usepackage{multirow}
\usepackage{csvsimple}
\usepackage{balance}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{nicefrac}
\usepackage{siunitx}
\usepackage{array,framed}
\usepackage{booktabs}
\usepackage{
  color,
  soul,
  float,
  epsfig,
  wrapfig,
  graphics,
  graphicx,
  subcaption
}
\usepackage{adjustbox}
\usepackage{csquotes}
\usepackage{cleveref}
\usepackage{dirtytalk}
\usepackage{textgreek}

@@

\newcommand{\todo}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\sys}{{\scshape Kv{\textalpha}sir}\xspace}
\newcommand{\rf}[1]{\ref{#1}}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\se}[1]{\S\ref{#1}}
\newcommand{\fg}[1]{Fig.~\ref{#1}}
\newcommand{\heading}[1]{\vspace{2pt}\noindent\textbf{\emph{#1}}:\enspace}
\newcommand{\ttt}[1]{\texttt{#1}\xspace}
\newcommand{\xxx}{\colorbox{red!30}{xxx}\xspace}

@@

\begin{abstract}
\end{abstract}
\maketitle

@@

This paper present \sys, a system for \emph{scalable program regeneration}.
\sys allows users
to express transformation goals declaratively, as logical constraints over
program properties such as input/output behavior, side-effect freedom, target
language, trace equivalence, or modular structure.
Given a source program and
such a query, \sys extracts a minimal set of relevant properties, guided by a
logic engine and a domain-specific knowledge base, and synthesizes a new
program that satisfies the desired constraints.

@@

Guided by these insights, \sys casts transformation as a constrained synthesis problem.
At its core is a property-driven pipeline: users express goals as logical constraints over semantic properties, such as input/output behavior, side-effect freedom, target language, or structural modularity.
\sys extracts a set of relevant properties, using a logic engine and domain-specific knowledge base, and synthesizes a new program that satisfies the specified constraints.
If no such program exists, \sys returns failure explanations derived from the unsatisfiable core.

@@

\heading{LLM-guided regeneration}
A structured prompt guides the language model, which performs the synthesis task.
The prompt is a composition of natural-language text fragments plugins contribute. 
A plugin can include domain-specific instructions as further guidance.
For example:
\begin{itemize}
  \item A \ttt{signature} plugin may contribute: \emph{\say{The output should implement a function \texttt{sqrt(n: float): float}.}}
  \item A \ttt{length} plugin combined with a minimization goal may prepend: \emph{\say{The output should be as short as possible while preserving the original functionality.}}
  \item A \ttt{javascript2haskell} plugin may prepend: \emph{\say{The output function should be written in Haskell.}}
\end{itemize}

@@

\begin{itemize}
  \item[\textbf{Q1}] \textbf{Correctness and Regeneration Quality}: Does \sys preserve program behavior and produce high-quality programs?
  \item[\textbf{Q2}] \textbf{Transformation Success}: Can \sys handle a diverse set of regeneration goals?
  \item[\textbf{Q3}] \textbf{Planning Efficiency \& Precision}: Does minimizing extracted properties help regeneration succeed faster and more reliably?
\end{itemize}

@@

We evaluate \sys on six benchmark suites, summarized in \cref{tab:benchmarks}.
These benchmarks include popular codebases from real-world package ecosystems, obfuscated or malicious components, and handcrafted microbenchmarks that reflect the use cases discussed in \cref{sec:example}.

\begin{table}[h]
\centering
  \caption{\textbf{Benchmark summary}. 
  Benchmark programs come from online repositories, public archives, security research datasets, and often referenced examples in programming culture.
  The $N$ column shows the number of programs/functions from each benchmar.
  }
\begin{tabular}{llrl}
\toprule
Benchmark                                               & Description                    & $N$ & Source \\
\midrule
  Rosetta Code                                          & Programming tasks              & 4 & \cite{rosettacode} \\
  npm utilities                                           & Utilities from npm             & 10 & \cite{regbench2025} \\
Python utilities                                        & Utilities from PyPi            & 1 & \cite{regbench2025} \\
  SSCA                                                    & Sneaky SSAs    & 3 & \cite{ev:eurosec:2022, es1, ohm2020backstabber} \\
  IOCCC                                                   & Obfuscated C code              & 2 & \cite{ioccc} \\
Microbenchmarks                                         &          & 3    & \\
  \hspace{.5em} \ttt{flatmap-stream}                      & Secure regeneration            &      & \cite{es1}  \\
  \hspace{.5em} \ttt{Q\_rsqrt}                             & C refactoring        &      & \cite{fast_inv_sqrt}  \\
  \hspace{.5em} \textsf{MusicDB}                          & Modularization           &      & \cite{codewithsadeemusicplayer} \\
\bottomrule
\end{tabular}
\label{tab:benchmarks}
\end{table}

Each task consists of an input program, a \sys query expressing desired properties, and a test suite or functional oracle.

@@

\begin{table}[h]
  \centering
  \caption{Correctness: Percentage of tasks passing all I/O tests}
  \begin{tabular}{lc}
    \toprule
    Benchmark & \sys Pass Rate \\ 
    \midrule
    Rosetta Code & \xxx/\xxx  \\
    npm Utilities & \xxx/\xxx \\
    Python Utilities & \xxx/\xxx \\
    SSCA & \xxx/\xxx  \\
    IOCCC & \xxx/\xxx  \\
    Microbenchmarks & \xxx/\xxx  \\
    \bottomrule
  \end{tabular}
\end{table}

\subsection{Q2: Transformation Success}

We test whether \sys meets transformation goals across different categories.
Each row corresponds to a class of transformation query (e.g., removal of side effects, modular decomposition).
We count success when the generated program meets all stated properties and passes correctness checks.
\sys consistently succeeds at expressing non-trivial goals that GPT-4 baseline prompts often fail to satisfy.

@@

To evaluate the impact of \sys's property planning, we compare it against a GPT-4 baseline that performs prompt-only rewriting without explicit access to guiding properties.

@@

\begin{table}[h]
  \centering
  \caption{
    Planning precision: Number of tasks where the synthesized program satisfies positive properties ($P_p$) and avoids negative properties ($P_n$).
  }
  \begin{tabular}{lcc}
    \toprule
    Variant & $P_{p}$ & $P_{n}$  \\
    \midrule
    \sys & \xxx & \xxx \\
    GPT-4 & \xxx & \xxx \\
    \bottomrule
  \end{tabular}
\end{table}

\sys consistently satisfies more of the declared properties while avoiding
unintended behaviors. For instance, in the \texttt{flatmap-stream} benchmark,
GPT-4 often inclduded malicious side effects when the code appeared innocuous,
whereas \sys generated provably pure rewrites by treating the source as
untrusted and grounding regeneration in I/O behavior alone.
Across all benchmarks, the planning step completes in under \xxx ms on average.
% TODO: re-add this
% adding negligible latency compared to synthesis time. Moreover, by minimizing
% the number of properties to extract and verify, planning reduces the total time
% and resource usage of the regeneration pipeline.

@@

\section{Discussion and Limitations}

@@

\heading{LLM limitations}
The generative synthesis phase is subject to the inherent variability and failure modes of large language models. These include hallucinations, sensitivity to prompt phrasing, and inconsistency under minor input changes.
\sys does not mitigate these risks, but allows their detection through post-hoc verification.
In cases where the system finds no satisfactory candidate, regeneration may fail and require manual intervention.

@@

\heading{Future directions}
Extensions that could improve \sys's capabilities include richer property languages (\eg temporal or dataflow properties), tighter integration with formal verification tools, and cross-component reasoning for coordinated rewrites.
Additionally, integrating counterfactual generation techniques~\cite{Cabalar_2020} could help explain why certain regeneration goals are infeasible or conflicting.

@@

\section{Conclusion}

>>>>

\usepackage{setspace}
\usepackage{enumerate}
\usepackage{algorithm2e}
\usepackage{algpseudocode}
\usepackage{graphics}
\usepackage{xparse} 
\usepackage{xspace}
\usepackage{multirow}
\usepackage{csvsimple}
\usepackage{balance}
\usepackage{minted}
\usepackage{xcolor}
\usepackage{nicefrac}
\usepackage{siunitx}
\usepackage{array,framed}
\usepackage{booktabs}
\usepackage{color}
\usepackage{soul}
\usepackage{float}
\usepackage{epsfig}
\usepackage{wrapfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{adjustbox}
\usepackage{csquotes}
\usepackage{cleveref}
\usepackage{dirtytalk}
\usepackage{textgreek}

@@

\def\gptmodel{{GPT-4o}\xspace}

\newcommand{\todo}[1]{\hl{\textbf{TODO:} #1}\xspace}
\newcommand{\sys}{{\scshape Kv{\textalpha}sir}\xspace}
\newcommand{\rf}[1]{\ref{#1}}
\newcommand{\sx}[1]{(\S\ref{#1})}
\newcommand{\cf}[1]{(\emph{Cf}.\S\ref{#1})}
\newcommand{\se}[1]{\S\ref{#1}}
\newcommand{\fg}[1]{Fig.~\ref{#1}}
\newcommand{\heading}[1]{\vspace{2pt}\noindent\textbf{\emph{#1}}:\enspace}
\newcommand{\ttt}[1]{\texttt{#1}\xspace}
\newcommand{\xxx}{\colorbox{red!30}{xxx}\xspace}
\newcommand{\promptbox}[1]{\hspace*{-0.0135\columnwidth}\fbox{\parbox[t]{0.95\columnwidth}{\tt{#1}}}}

@@

\begin{abstract}
Modern software systems are constantly evolving—requiring developers to
  refactor legacy code, adapt to changing APIs, translate across languages, and
  patch security vulnerabilities. These transformations are often brittle,
  manual, and error-prone. Large language models (LLMs) offer new opportunities
  for automating such tasks, but their outputs are shaped by surface cues, lack
  semantic guarantees, and require brittle prompting strategies. This paper
  presents \sys, a system for controllable program regeneration that combines
  logic-based planning with LLM-guided synthesis.
  By expressing transformation
  goals as declarative constraints over program properties---such as input/output
  behavior, side-effect freedom, language, or modular structure, \sys
  regenerates code that satisfies explicit semantic requirements.
  We demonstrate \sys across a wide range of tasks, including security
  hardening, language translation, and idiomatic rewriting, and highlight its
  ability to deliver interpretable, high-quality transformations with minimal
  developer guidance.
\end{abstract}
\maketitle

@@

This paper present \sys, a system for \emph{controllable program regeneration}.
\sys allows users
to express transformation goals declaratively, as logical constraints over
program properties such as input/output behavior, side-effect freedom, target
language, trace equivalence, or modular structure.
Given a source program and
such a query, \sys extracts a minimal set of relevant properties, guided by a
logic engine and a domain-specific knowledge base, and synthesizes a new
program that satisfies the desired constraints.

@@

Guided by these insights, \sys casts transformation as a constrained synthesis problem.
At its core is a property-driven pipeline: users express goals as logical constraints over semantic properties, such as input/output behavior, side-effect freedom, target language, or structural modularity.
\sys extracts a set of relevant properties, derived from its logic engine and a domain-aware knowledge base, and synthesizes a new program that satisfies the specified constraints.
If no such program exists, \sys returns a failure explanation from the unsatisfiable core.

@@

\heading{LLM-guided regeneration}
A structured prompt guides the language model, which performs the synthesis task.
The prompt is a composition of natural-language text fragments plugins contribute. 
A plugin can include domain-specific instructions as further guidance.
For example:
A \ttt{signature} plugin may contribute:

 \promptbox{
   {The output should implement a function \texttt{sqrt(n: float): float}.}
 }
A \ttt{length} plugin combined with a minimization goal may prepend:

\promptbox{
  {The output should be as short as possible while preserving the original functionality.}
}
A \ttt{javascript2haskell} plugin may prepend:

\promptbox{
  {The output function should be written in Haskell.}
}

@@

\begin{itemize}
  \item[\textbf{Q1}] \textbf{Correctness and Regeneration Quality}: Does \sys preserve program behavior and produce high-quality programs?
  \item[\textbf{Q2}] \textbf{LLM Baseline}: How does \sys compare to naively prompting a large language model?
  \item[\textbf{Q3}] \textbf{Planning Efficiency \& Precision}: Does minimizing extracted properties help regeneration succeed faster and more reliably?
    % TODO: Maybe make naive LLM Q3 and merge Q3 and Q2.
\end{itemize}

@@

We evaluate \sys on six benchmark suites, summarized in \cref{tab:benchmarks}.
Each task consists of an input program, a \sys query expressing desired
properties, and a test suite or functional oracle.
The Rosetta Code~\cite{rosettacode} benchmarks include four programming tasks written in four different
languages each (Python, JavaScript, C, and Haskell). 
These include classic programs that do not require any language-specific features to implement.
These are: the classic \emph{Hello, World!} program as found in most programming tutorials,
a program that applies the ROT-13 cipher to a string,
a program that computes the median of a list of numbers,
and a program that reads a file and prints its contents to the console line-by-line.
The npm benchmark includes ten popular (100.000+ weekly downloads) npm packages that implement utility
functionality such as string manipulation, data structure transformations, and math.
Similalry, the PyPi utilities benchmark includes three functions sourced from PyPi that implement similar functionality.
The SSCA dataset includes three sneaky supply-chain attacks that obfuscate malicious behavior in otherwise innocuous-looking code.
The attack activates under specific environment conditions, such as the presence of a specific environment variable or specific inputs
getting passed to the program. The attacks involve private key exfiltration~\cite{ohm2020backstabber}, Bitcoin private key theft~\cite{ev:eurosec:2022}, and an SSH backdoor installation~\cite{copeland2019frightening}.
and occur while the program still performs its advertised functionality.
The IOCCC benchmark includes two programs from the International Obfuscated C Code Contest (IOCCC)~\cite{ioccc}.
These programs are intentionally obfuscated, using advanced techniques such as bit manipulation, undefined behavior,
and exploitation of the C preprocessor and the lax parsing rules of the C language.
These programs perform mathematical computations like mersense primality testing and adding two numbers.
Finally, the microbenchmarks include three programs that implement the regeneration tasks discussed in \cref{sec:example}.

\begin{table}[h]
\centering
  \caption{\textbf{Benchmark summary}. 
  Benchmark programs come from online repositories, public archives, security research datasets, and often referenced examples in programming culture.
  The $N$ column shows the number of programs/functions from each benchmar.
  }
\begin{tabular}{llrl}
\toprule
Benchmark                          & Description         & $N$ & Source \\
\midrule
Rosetta Code                       & Programming tasks   & 16   & \cite{rosettacode} \\
npm utilities                      & Utilities from npm  & 10  & \cite{regbench2025} \\
PyPi utilities                   & Utilities from PyPi & 3   & \cite{regbench2025} \\
SSCA                               & Sneaky SSAs         & 3   & \cite{ev:eurosec:2022, ohm2020backstabber,copeland2019frightening} \\
IOCCC                              & Obfuscated C code   & 2   & \cite{ioccc} \\
Microbenchmarks                    &                     & 3   & \\
\hspace{.5em} \ttt{flatmap-stream} & Secure regeneration &     & \cite{es1}  \\
\hspace{.5em} \ttt{Q\_rsqrt}       & C refactoring       &     & \cite{fast_inv_sqrt}  \\
\hspace{.5em} \textsf{rigidDB}     & Modularization      &     & \cite{codewithsadeemusicplayer} \\
\bottomrule
\end{tabular}
\label{tab:benchmarks}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{Correctness: Percentage of tasks passing all tests (when present) and manual inspection.}
  \begin{tabular}{lc}
    \toprule
    Benchmark & \sys Pass Rate \\ 
    \midrule
    Rosetta Code & 16/16  \\
    npm Utilities & 10/10 \\
    Python Utilities & 3/3\\
    SSCA & 3/3  \\
    IOCCC & 1/2 \\
    Microbenchmarks & 2.5/3  \\
    \bottomrule
  \end{tabular}
\end{table}

\sys succeeds in all of the Rosetta Code benchmarks, code is correct, we had to manually verify it as no test cases are available.
\sys regenerates correctly all npm and PyPi utilities, it does not introduce and sideffectful or malicious behavior.
The synthesized programs reveal several interesting insights and patterns.
\sys-generated code often lacks the optimizations commonly
implemented by library developers, such as early exits or caching.
For instance, the \texttt{left-pad} library, precomputes padding for strings below a certain length
and returns it directly. In contrast, \sys tends to produce straightforward
implementations without attempting similar optimizations.
\sys also omits domain-specific knowledge.
For example, in the \texttt{is} family of libraries,
\sys-generated code frequently fails to account for all edge cases,
and often misses JavaScript-specific patterns,
such as checking an object’s string representation to decide if an object is circular, as in the \texttt{is-circular} library.
\sys has weak performance on libraries that involve complex regexes or perform non-trivial math.
For the SSCA benchmarks, \sys successfully regenerates all three malicious libraries, removing the malicious behavior while preserving the original functionality.
For the flatmap-stream attack, \sys uses some domain-specific logic (encoded in its knowledge-base by the \ttt{js-stream} plugin) to generate a function that produces a node \ttt{Stream} object.
For the IOCCC benchmarks, \sys regenerates the \ttt{adder} program, which is a simple program that adds two numbers,
it also regenerates \ttt{mersenne} in regards that it correctly performs a naive mersenne primality testing, but it does not follow the non-obvious output scheme of the original program, which returns a non-zero hexadecimal number when $2^p - 1$ ($p$ being the input number) is not prime.
For the microbenchmarks, \sys correctly regenerates the \ttt{flatmap-stream} program, producing a safe Haskell version that is idiomatic and preserves the original functionality.
However, this version does not match exactly the semantics of the original one, as it operates over infinitely nested lists, rather than only one level deep ones.
The \ttt{Q\_rsqrt} program includes the obvious, idiomatic computation of the inverse square root ($1/\sqrt{x}$) rather than the original bit-level manipulation.
Finally, \sys successfully decomposes the \ttt{rigidDB} program into two
functions, \ttt{setupDatabase} and \ttt{getAlbumsByArtist}, which is a
modularization that preserves the original functionality and produce equivalent I/O and SQL traces.

\sys is able to regenerate programs that are correct and preserve the original functionality,
while also removing any malicious behavior or obfuscation.
Failure cases highlight current limitations, and inspire future work~(\cref{sec:discussion}).

\subsection{Q2: Naive LLM vs. \sys}

To compare \sys against a baseline, we use a \gptmodel instance
that performs prompt-only rewriting without explicit access to guiding properties.
The LLM gets the following prompt template:

\promptbox{
  \emph{Task description} \eg {Give back the same code having removed any vulnuerabilities}\\

  Program:\\
  \emph{Program/function source code}\\

  Please return the program's source code after performing the task.
}

For the Rosetta Code benchmarks, \gptmodel 
succesful in all language translation tasks.
The original and LLM-generated code matches the semantics
of the original one, confirmed after manually inspecting the generated code.
Similarly, the LLM was succesful in transforming the npm and PyPi utilities towards
removing any vulnerabilities from them, as they are benign and the transformation
involved the LLM simply repeating the original code without any changes.
The SSCA benchmark tasks are more interesting, as they involve 
malicious code. For the malicious libraries, we provide the LLM 
with two different versions. One is the original high-profile attack that appeared on npm,
with the second one being an attack that is semantically equivalent but with the source 
having gone through an iterative loop where a second LLM is tasked with making the code ostensibly 
secure. This involves adding integrity checks at all points in the program where a value is used.
\gptmodel was succesful in eliminating the original attacks, but failed in \emph{all} 
cases where the source code was particulalry crafted to appear secure, regenerating both 
the original functionality and the attack.
For the IOCCC benchmarks, \gptmodel also fails 
in both cases to regenerate the programs in a way where the code's 
functionality is preserved while removing the obfuscation.
The \ttt{adder} program is regenerated as a program that prints the \ttt{argc} argument, 
while the \ttt{mersenne} program performs irrelevant arithmetic operations that 
resemble the original source, and fails to even compile.
For the microbenchmarks, \gptmodel is able to regenerate the \ttt{flatmap-stream} program, but fails to produce a Haskell version of it,
as it overfits to the original JavaScript source code which uses the \ttt{Stream} API,
and fails to produce a Haskell program that is nor equivalent to the original, nor idiomatic.
For the \ttt{Q\_rsqrt} program, \gptmodel fails to produces a program that idiomatically 
computes the inverse square root, rather trying to minimize the number of lines in the program
by removing constants and comments and still keeping the bit-level manipulation.
Finally, for the \ttt{rigidDB} program, \gptmodel is able to decompose the original program into two functions
and names them \ttt{setupDatabase} and \ttt{getAlbumsByArtist}.

\sys consistently outperforms a \gptmodel baseline,
highlighting the inherent weaknesses of a purely prompt-based approach.

@@

To evaluate the impact of \sys's property planning, we compare it against a \gptmodel baseline that performs prompt-only rewriting without explicit access to guiding properties.

@@

% \begin{table}[h]
%   \centering
%   \caption{
%     Planning precision: Number of tasks where the synthesized program satisfies positive properties ($P_p$) and avoids negative properties ($P_n$).
%   }
%   \begin{tabular}{lcc}
%     \toprule
%     Variant & $P_{p}$ & $P_{n}$  \\
%     \midrule
%     \sys & \xxx & \xxx \\
%     \gptmodel & \xxx & \xxx \\
%     \bottomrule
%   \end{tabular}
% \end{table}

\sys consistently satisfies more of the declared properties while avoiding
unintended behaviors. For instance, in the \texttt{flatmap-stream} benchmark,
\gptmodel often inclduded malicious side effects when the code appeared innocuous,
whereas \sys generated pure rewrites by treating the source as
untrusted and grounding regeneration in I/O behavior alone.
Across all benchmarks, the planning step completes in under 50ms on average.
Similalry, in the \ttt{Q\_rsqrt} benchmark, \gptmodel often produces bit-level
manipulations that are not idiomatic in Haskell, while \sys generates a simple
and idiomatic Haskell function that computes the inverse square root.
This is guided by the fact the \sys extracts and provides to its backend model only the function signature 
and length of the program, which it minimizes, without including the original source code,
which as shown in the experimental results makes the model overfit its regeneration to it.
\sys's I/O pair extraction also provides confidence that 
the regenerated program has the same client-visible behavior as the original one, while 
prompting a model like \gptmodel would always require manual inspection or the presence 
of developer tests to verify the correctness of the regeneration.

@@

\section{Discussion and Limitations}
\label{sec:discussion}

@@

\heading{LLM limitations}
The generative synthesis phase
is subject to the inherent variability and failure modes
of large language models.
These include hallucinations,
sensitivity to prompt phrasing,
and inconsistency
under minor input changes.
\sys does not mitigate these risks,
but allows their detection
through post-hoc verification.
In cases where the system finds no satisfactory candidate,
regeneration fails.

@@

\heading{Future directions}
Extensions that could improve \sys's capabilities include richer property languages (\eg temporal or dataflow properties~\cite{azzopardi2023ltl,handa2021orderawaredataflowmodelparallel}), tighter integration with formal verification tools, and cross-component reasoning for coordinated rewrites.
Furthermore, performance-oriented transformations could be potent additions, allowing \sys to transform the program across dimensions like runtime, parallelizability, or memory usage.
Additionally, integrating counterfactual generation techniques~\cite{Cabalar_2020} could help explain why certain regeneration goals are infeasible or conflicting.

@@

\section{Conclusion}
This paper introduced \sys, a system for property-guided program regeneration
that bridges the flexibility of large language models with the precision of
logic-driven planning.
By allowing developers to declaratively specify
transformation goals as logical constraints, \sys elevates LLM-assisted program
trasnformations to a controllable, interpretable, and iterative synthesis-verification
process.
Evaluation demonstrates that \sys produces high-quality regenerations
across diverse tasks, outperforming naive prompting baselines in correctness,
controllability, and resilience to adversarial or obfuscated inputs.

\sys opens the door to a new class of synthesis tools that combine symbolic
reasoning and neural generation under a unified, extensible framework.
As program synthesis systems grow increasingly reliant on LLMs, we believe the
future lies in harnessing their generative power within a framework that retains
correctness, explainability, and developer control as first-class citizens.
